%% This defines the bibliography file (main.bib) and the bibliography style.
%% If you want to create a bibliography file by hand, change the contents of
%% this file to a `thebibliography' environment.  For more information 
%% see section 4.3 of the LaTeX manual.

\begin{thebibliography}{99}
\begin{singlespace}
\raggedright

\bibitem{windows-docker}
``Docker CTO: Why Microsoft's Docker plans for Windows will matter to you," October 28, 2014. Available: \url{http://www.zdnet.com/docker-cto-why-microsofts-docker-plans-for-windows-will-matter-to-you-7000035150/}.
`
\bibitem{lxc}
``PaaS under the hood, episode 1: kernel namespaces," November 28, 2012. Available: \url{http://blog.dotcloud.com/under-the-hood-Linux-kernels-on-dotcloud-part}.

\bibitem{dockerregistry}
``Docker Hub Registry," [Online]. Available: \url{https://registry.hub.docker.com}.

\bibitem{baseimage}
``Creating a Base Image," 2014. [Online]. Available: \url{https://docs.docker.com/articles/baseimages/}.

\bibitem{dockerregistry-github}
``Docker Registry," 2014. [Online]. Available: \url{https://github.com/docker/docker-registry}.

\bibitem{devops}
``Docker: The first true devops tool?" 2014. [Online]. Available: \url{http://www.infoworld.com/article/2608674/application-development/application-development-docker-the-first-true-devops-tool.html}.

\bibitem{aws}
``AWS doubles down on Docker technology, launches EC2 container service," 2014. [Online]. Available: \url{http://www.zdnet.com/article/aws-doubles-down-on-docker-technology-launches-ec2-container-service/}.

\bibitem{vmware}
``VMware + Containers = Containers without Compromise," 2014. [Online]. Available: \url{http://blogs.vmware.com/cto/vmware-containers-containers-without-compromise/}.

\bibitem{flockport}
``Flockport Rivals Docker with Open Source Container Virtualization," 2014. [Online]. Available: \url{http://thevarguy.com/virtualization-applications-and-technologies/091614/flockport-rivals-docker-open-source-container-virtualiz}.

\bibitem{rocket}
``CoreOS is building a container runtime, Rocket," 2014. [Online]. Available: \url{https://coreos.com/blog/rocket/}.

\bibitem{lxd}
``Ubuntu LXD: Not a Docker replacement, a Docker enhancement," 2014. [Online]. Available: \url{http://www.zdnet.com/article/ubuntu-lxd-not-a-docker-replacement-a-docker-enhancement/}.

\bibitem{pvc}
``Converting Virtual Containers, Virtual Machines, and Hardware Nodes to each other," 2014. [Online]. Available: \url{http://kb.sp.parallels.com/en/6324}.

\bibitem{pvcloses}
``Parallels to adopt Docker as native app format in Cloud Server," 2014. [Online]. Available: \url{http://www.theregister.co.uk/2014/12/15/parallels_to_adopt_docker_as_native_app_format_in_cloud_server/}.

\bibitem{performance}
M. G. Xavier, M. V. Neves, F. D. Rossi, T. C. Ferreto, T. Lange, and C. A. F. De Rose, ``Performance Evaluation of Container-based Virtualization for High Performance Computing Environments," 2013. [Online]. Available: \url{http://marceloneves.org/papers/pdp2013-containers.pdf}.

\bibitem{vmotion}
``VMware vMotion: Virtual Machine Live Migration," [Online]. Available: \url{http://www.vmware.com/products/vsphere/features/vmotion}.

\bibitem{DRS}
``vSphere Dynamic Resource Scheduler \& Distributed Power Management," [Online]. Available: \url{http://www.vmware.com/products/vsphere/features/drs-dpm}.

\bibitem{CRIU}
``CRIU," 2014. [Online]. Available: \url{http://criu.org/}.

\bibitem{debootstrap}
``Debootstrap," [Online]. Available: \url{https://wiki.debian.org/Debootstrap}.

\bibitem{fig}
``Fig | Fast, isolated development environments using Docker," 2014. [Online]. Available: \url{http://www.fig.sh}.

\bibitem{kubernetes}
``Kubernetes," 2014. [Online]. Available: \url{https://github.com/GoogleCloudPlatform/kubernetes}.

\bibitem{fleet}
``Launching Containers with fleet," 2014. [Online]. Available: \url{http://coreos.com/docs/launching-containers/launching/launching-containers-fleet/}.

\bibitem{dockerindocker}
``Docker can now run within docker," 2013. [Online]. Available: \url{https://blog.docker.com/2013/09/docker-can-now-run-within-docker/}.

\bibitem{dockercompose}
``Docker Announces Orchestration for Multi-Container Distributed Apps," 2014. [Online]. Available: \url{https://blog.docker.com/2014/12/docker-announces-orchestration-for-multi-container-distributed-apps/}.

\bibitem{scarab}
``Scarab: A system to patch your content files," 2013. [Online]. Available: \url{https://github.com/loyso/Scarab}.

\bibitem{trustedbuilds}
``Introducing Trusted Builds," 2013. [Online]. Available: \url{https://blog.docker.com/2013/11/introducing-trusted-builds/}.

\end{singlespace}
\end{thebibliography}
